---
title: "Individual Assignment 8"
author: "Margot Lai(499100)"
date: "11/6/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Problem #8: In the lab, a classification tree was applied to the Carseats data set after converting Sales into a qualitative response variable. Now we will seek to predict Sales using regression trees and related approaches, treating the response as a quantitative variable.

(d) Use the bagging approach in order to analyze this data. What test MSE do you obtain? Use the importance() function to determine which variables are most important.
```{r}
library(tree)
library(ISLR)
attach(Carseats)
library(randomForest)
set.seed(1)
train = sample(1:nrow(Carseats), nrow(Carseats)/2)
car.train = Carseats[train, ]
car.test = Carseats[-train, ]
bag.car = randomForest(Sales ~ ., data = Carseats, subset = train, mtry = 10,
                        importance = TRUE)
bag.car
predict.bag = predict(bag.car, newdata = car.test)
mean((predict.bag - car.test$Sales)^2)
importance(bag.car)
varImpPlot(bag.car)
#The test MSE is 2.623527
#Price       55.1387362     500.32765
#ShelveLoc   46.3295341     376.78200
#These two are the most important varibles as the graph show.
```

(e) Use random forests to analyze this data. What test MSE do you obtain? Use the importance() function to determine which variables are most important. Describe the effect of m, the number of variables considered at each split, on the error rate obtained.

```{r}
#when m=1, test mse = 4.747522
set.seed(1)
rf.car1 = randomForest(Sales ~ ., data = Carseats, subset = train, mtry = 1,
                        importance = TRUE)
set.seed(1)
pred.rf1 = predict(rf.car1, newdata = car.test)
mean((pred.rf1 - car.test$Sales)^2)

#when m=2, test mse = 3.401523
set.seed(1)
rf.car2 = randomForest(Sales ~ ., data = Carseats, subset = train, mtry = 2,
                        importance = TRUE)
set.seed(1)
pred.rf2 = predict(rf.car2, newdata = car.test)
mean((pred.rf2 - car.test$Sales)^2)

#when m=3, test mse = 2.960559
set.seed(1)
rf.car3 = randomForest(Sales ~ ., data = Carseats, subset = train, mtry = 3,
                        importance = TRUE)
set.seed(1)
pred.rf3 = predict(rf.car3, newdata = car.test)
mean((pred.rf3 - car.test$Sales)^2)

#when m=4, test mse = 2.787584
set.seed(1)
rf.car4 = randomForest(Sales ~ ., data = Carseats, subset = train, mtry = 4,
                        importance = TRUE)
set.seed(1)
pred.rf4 = predict(rf.car4, newdata = car.test)
mean((pred.rf4 - car.test$Sales)^2)

#when m=5, test mse = 2.714168
set.seed(1)
rf.car5 = randomForest(Sales ~ ., data = Carseats, subset = train, mtry = 5,
                        importance = TRUE)
set.seed(1)
pred.rf5 = predict(rf.car5, newdata = car.test)
mean((pred.rf5 - car.test$Sales)^2)

#when m=6, test mse = 2.667767
set.seed(1)
rf.car6 = randomForest(Sales ~ ., data = Carseats, subset = train, mtry = 6,
                        importance = TRUE)
set.seed(1)
pred.rf6 = predict(rf.car6, newdata = car.test)
mean((pred.rf6 - car.test$Sales)^2)


# As m get larger, the test MSE get smaller and smaller
importance(rf.car1)
varImpPlot(rf.car1)

#As we can see the most important variables are price and shelveloc in bagging model as random forest too.
```
Problem #10: We now use boosting to predict Salary in the Hitters data set.

(a) Remove the observations for whom the salary information is unknown, and then log-transform the salaries.

```{r}
Hitters = na.omit(Hitters)
Hitters$Salary = log(Hitters$Salary)
```

(b) Create a training set consisting of the first 200 observations, and a test set consisting of the remaining observations.

```{r}
train = 1:200
Hitters.train = Hitters[train, ]
Hitters.test = Hitters[-train, ]
```

(c) Perform boosting on the training set with 1,000 trees for a range of values of the shrinkage parameter λ. Produce a plot with different shrinkage values on the x-axis and the corresponding training set MSE on the y-axis.

```{r}
library(gbm)
set.seed(1)
pows = seq(-10, -0.2, by = 0.1)
lambdas = 10^pows
train.err = rep(NA, length(lambdas))
for (i in 1:length(lambdas)) {
    boost.hitters = gbm(Salary ~ ., data = Hitters.train, distribution = "gaussian", n.trees = 1000, shrinkage = lambdas[i])
    pred.train = predict(boost.hitters, Hitters.train, n.trees = 1000)
    train.err[i] = mean((pred.train - Hitters.train$Salary)^2)
}
plot(lambdas, train.err, type = "b", xlab = "Shrinkage values", ylab = "Training MSE")
```

(d) Produce a plot with different shrinkage values on the x-axis and the corresponding test set MSE on the y-axis.

```{r}
set.seed(1)
test.err = rep(NA, length(lambdas))
for (i in 1:length(lambdas)) {
    boost.hitters = gbm(Salary ~ ., data = Hitters.train, distribution = "gaussian", n.trees = 1000, shrinkage = lambdas[i])
    yhat = predict(boost.hitters, Hitters.test, n.trees = 1000)
    test.err[i] = mean((yhat - Hitters.test$Salary)^2)
}
plot(lambdas, test.err, type = "b", xlab = "Shrinkage values", ylab = "Test MSE")
min(test.err)
lambdas[which.min(test.err)]
#The minimum test MSE is 0.2540265 and the lambda=0.07943282
```

(e) Compare the test MSE of boosting to the test MSE that results from applying two of the regression approaches seen in Chapters 3 and 6.

```{r}
#linear regression
library(glmnet)
fit1 = lm(Salary ~ ., data = Hitters.train)
pred1 = predict(fit1, Hitters.test)
mean((pred1 - Hitters.test$Salary)^2)

#boosting
x = model.matrix(Salary ~ ., data = Hitters.train)
x.test = model.matrix(Salary ~ ., data = Hitters.test)
y = Hitters.train$Salary
fit2 = glmnet(x, y, alpha = 0)
pred2 = predict(fit2, s = 0.01, newx = x.test)
mean((pred2 - Hitters.test$Salary)^2)

#The test MSE of boosting is lower than linear regression and ridge regression.
```

(f) Which variables appear to be the most important predictors in the boosted model?

```{r}
library(gbm)
boost.hitters <- gbm(Salary ~ ., data = Hitters.train, distribution = "gaussian", n.trees = 1000, shrinkage = lambdas[which.min(test.err)])
summary(boost.hitters)
#CAtBat is the most important variable
```

(g) Now apply bagging to the training set. What is the test set MSE for this approach?

```{r}
set.seed(1)
bag.hitters <- randomForest(Salary ~ ., data = Hitters.train, mtry = 19, ntree = 500)
yhat.bag <- predict(bag.hitters, newdata = Hitters.test)
mean((yhat.bag - Hitters.test$Salary)^2)
#bagging test MSE is 0.2299324, lower than boosting
```
