---
title: "Individual Assignment 7"
author: "Margot Lai(499100)"
date: "10/29/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Problem #8: In the lab, a classification tree was applied to the Carseats data set after converting Sales into a qualitative response variable. Now we will seek to predict Sales using regression trees and related approaches, treating the response as a quantitative variable.

(a) Split the data set into a training set and a test set.

```{r}
library(tree)
library(ISLR)
attach(Carseats)
set.seed(100)
train = sample(1:nrow(Carseats), nrow(Carseats)/2)
car.train = Carseats[train,]
car.test = Carseats[-train,]
```

(b) Fit a regression tree to the training set. Plot the tree, and interpret the results. What test MSE do you obtain?

```{r}
car.tree = tree(Sales~.,data = car.train)
plot(car.tree)
text(car.tree, pretty = 0)
summary(car.tree)
car.tree
##Interpretation: Price, CompPrice and Age are the terminal nodes, shelveloc is the most important indicator of sales, and price will be classified based on age predictor.

yhat = predict(car.tree,newdata = car.test)
mean((yhat - car.test$Sales)^2)
#Test MSE is 5.395751
```

(c) Use cross-validation in order to determine the optimal level of tree complexity. Does pruning the tree improve the test MSE?

```{r}
set.seed(100)
car.cv = cv.tree(car.tree)
plot(car.cv$size, car.cv$dev, type = "b")
plot(car.cv$k, car.cv$dev, type = "b")
#Size 8 nodes is the best
```
```{r}
prune.car = prune.tree(car.tree, best = 8)
plot(prune.car)
text(prune.car,pretty=0)

predict.prune = predict(prune.car, newdata = car.test)
mean((predict.prune - car.test$Sales)^2)
#The MSE slightly decrease from 5.395751 to 5.32676 after prued, pruning the tree improved the test MSE.
```

 
