---
title: "Individual Assignment 9"
author: "Margot Lai(499100)"
date: "11/14/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Exercises 9.7
Problem #8. This problem involves the OJ data set which is part of the ISLR package. 

(a) Create a training set containing a random sample of 800 observations, and a test set containing the remaining observations.
```{r}
library(ISLR)
attach(OJ)
set.seed(1)
train=sample(dim(OJ)[1], 800)
train.OJ=OJ[train,]
test.OJ=OJ[-train,]
```
(b) Fit a support vector classifier to the training data using cost=0.01, with Purchase as the response and the other variables as predictors. Use the summary() function to produce summary statistics, and describe the results obtained.
```{r}
library(e1071)
svm.linearOJ<- svm(Purchase ~ ., kernel='linear',  data=train.OJ, cost=0.01)
summary(svm.linearOJ)
#There are total 435 support vectors, 219 of them are Citurus Hill and 216 of them are Minute Maid.
```
(c) What are the training and test error rates?
```{r}
#training error rate is 17.5%
train.pred=predict(svm.linearOJ, train.OJ)
table(train.OJ$Purchase, train.pred)
mean(train.pred!= train.OJ$Purchase)
#test error rate is 17.78%
test.pred=predict(svm.linearOJ, test.OJ)
table(test.OJ$Purchase, test.pred)
mean(test.pred != test.OJ$Purchase)
```
(d) Use the tune() function to select an optimal cost. Consider values in the range 0.01 to 10.
```{r}
tune.OJ=tune(svm, Purchase ~ ., data=train.OJ, kernel='linear', ranges=list(cost=10^seq(-2,1, by=.5)))
summary(tune.OJ)
```
(e) Compute the training and test error rates using this new value for cost.
```{r}
newsvm.linearoj=svm(Purchase ~ ., kernel='linear', data=train.OJ, cost=tune.OJ$best.parameters$cost)
train.pred=predict(newsvm.linearoj, train.OJ)
table(train.OJ$Purchase, train.pred)
mean(train.pred != train.OJ$Purchase)
#train error rate is 16.37%
test.pred=predict(newsvm.linearoj, test.OJ)
table(test.OJ$Purchase, test.pred)
mean(test.pred != test.OJ$Purchase)
#test error rate is 14.81%
```
(f) Repeat parts (b) through (e) using a support vector machine with a radial kernel. Use the default value for gamma.
```{r}
svm.radialoj<-svm(Purchase~ ., kernel='radial', data=train.OJ )
summary(svm.radialoj)
train.pred<-predict(svm.radialoj, train.OJ)
table(train.OJ$Purchase, train.pred)
mean(train.pred != train.OJ$Purchase)
#The train error rate is 18.52%
test.pred<-predict(svm.radialoj, test.OJ)
table(test.OJ$Purchase, test.pred)
mean(test.pred != test.OJ$Purchase)
#The test error rate is 15.88%
```

```{r}
tunerad.OJ<-tune(svm, Purchase ~ ., data=train.OJ, kernel='radial', ranges=list(cost=10^seq(-2,1, by=.5)))
summary(tunerad.OJ)
newsvm.radialoj<-svm(Purchase ~ ., kernel='radial', data=train.OJ, cost=tunerad.OJ$best.parameters$cost)
train.pred<-predict(newsvm.radialoj, train.OJ)
table(train.OJ$Purchase, train.pred)
mean(train.pred != train.OJ$Purchase)
#The train error rate from selected optimal cost is 15.13%
test.pred<-predict(newsvm.radialoj, test.OJ)
table(test.OJ$Purchase, test.pred)
mean(test.pred != test.OJ$Purchase)
#The test error rate from selected optimal cost is 18.52 slightly increase than default gamma
```
(g) Repeat parts (b) through (e) using a support vector machine with a polynomial kernel. Set degree=2.
```{r}
svm.polyoj<-svm(Purchase~ ., kernel='polynomial', data=train.OJ, degree=2 )
summary(svm.polyoj)
train.pred<-predict(svm.polyoj, train.OJ)
table(train.OJ$Purchase, train.pred)
mean(train.pred != train.OJ$Purchase)
#The train error rate is 18.25%
test.pred<-predict(svm.polyoj, test.OJ)
table(test.OJ$Purchase, test.pred)
mean(test.pred != test.OJ$Purchase)
#The test error rate is 22.22%
```

```{r}
tunepoly.OJ<-tune(svm, Purchase ~ ., data=train.OJ, kernel='polynomial', degree=2, ranges=list(cost=10^seq(-2,1, by=.5)))
summary(tunepoly.OJ)
#cost the 10 is the optimal cost
newsvm.polyoj<-svm(Purchase ~ ., kernel='polynomial', data=train.OJ, degree=2, cost=tunerad.OJ$best.parameters$cost)
train.pred<-predict(newsvm.polyoj, train.OJ)
table(train.OJ$Purchase, train.pred)
mean(train.pred != train.OJ$Purchase)
#The train error rate of cost=10 is 18.5%
test.pred<-predict(newsvm.polyoj, test.OJ)
table(test.OJ$Purchase, test.pred)
mean(test.pred != test.OJ$Purchase)
#The test error rate of cost=10 is 22.96%.
detach(OJ)
```
```
(h) Overall, which approach seems to give the best results on this data?

Overall the approach that give the best results on this data is the training and test error rate with the new value of cost on both training and test data.